An Open Platform for Managing Short Programming Exercises

### 2013-06-20 paper/paper.tex
rewrite motivations for creating CloudCoder

Recent years have seen an explosion of online services for learning
to program:  Udacity \cite{udacity}, Codecademy \cite{codeacademy},
ProgZoo \cite{progzoo}, 
Codingbat \cite{codingbat}, Coursera \cite{coursera}, Turingscraft
\cite{turingscraft}, Problets \cite{Kumar:2005:GPA:1163405.1163408}, CS Circles \cite{Pritchard:2013:CCI:2445196.2445370} and
several others.  These systems are very powerful, and show great promise to
improve introductory computer science.  Given all of these
very good systems, one may ask why we thought it a good career move
to build yet another system.  There are three main reasons:

%\begin{itemize}

%\item 
First, we wanted a system that an instructor can easily integrate into an existing traditional course.
  Many massive open online courses (MOOCs), such those available through Udacity and
  Coursera, were not designed for a traditional classroom and cannot be easily incorporated into an existing course.  
  The infrastructure provided by a MOOC is geared towards the course
  taught through the MOOC, and is not really configurable or customizable.

 % systems, such as Udacity, Coursera, and CodeAcademy, are
 %  massive open online courses (MOOCs) that cannot be easily
 %  incorporated into a traditional classroom setting.  MOOCs can be wonderfully
 %  enriching for students who take these courses.  However, because
 %  MOOCs offer an entire
 %  course, whatever online programming infrastructure they provide is part of that
 %  course.

%\item 
Second, we wanted an open, customizable system that focuses on short programming exercises that students
  can solve in their browser, and receive immediate feedback.  There are excellent systems that help
  faculty manage longer programming assignments
  \cite{Edwards:2008:WAG:1384271.1384371}, or homework and review questions
  \cite{turingscraft, Kumar:2005:GPA:1163405.1163408}.  Codingbat
  \cite{codingbat} is a fantastic free service that provides short
  programming exercises, but it is not easily customizable and does not provide
  access to all of the submissions submitted by students.
  We see CloudCoder as a complementary component to these resources.

% Some existing systems, such as Problets \cite{Kumar:2005:GPA:1163405.1163408},  and Turingscraft
%   \cite{turingscraft}, provide homework exercises that can be incorporated
%   such as Codingbat \cite{codingbat},
%  , can be integrated into an existing course.
%   Codingbat, while free to use and fantastically useful, does not give faculty access to a very
%   rich data set

%\item
Finally, we wanted exercises that could be freely modified and
redistributed.  Much of the excellent content available through MOOCs,
or the increasing amount of digital content available through textbook publishers, 
cannot be modified or re-used outside of those contexts.  This can be a significant
impediment to researchers trying to study the difficulty level of
various exercises, or to build intelligent tutoring systems (ITSs)
that require a large bank of questions and their solutions.

%\end{itemize}

% There are two reasons.  First, many of
% these systems, such are Udacity, Coursera, and CodeAcademy, are
% massive open online courses (MOOCs).  MOOCs typically provide
% supporting infrastructure that helps students learn to code in their
% browsers, and the course material offered by a MOOC can be a wonderfully enriching
% experience for someone who enrolls in the course.  However, it is not
% clear how faculty who teach more traditional courses can
% integrate any of the infrastructure provided by a MOOC into
% their curriculum.  Second, 
% the systems that could be easily integrated into an existing course, such as
% Codingbat or Turingscraft, are
% are either commercial, or closed, or both.  To our knowledge, none of
% these systems readily support faculty who want to 
% modify the code, host their own installation, extract data about
% student behaviors beyond the basic correctness of their submissions,
% or redistribute the programming exercises and assignments.

We believe the academic community should have a fully open alternative
to the closed and/or commercial systems that have exploded onto the CS
Education scene.  Faculty can integrate CloudCoder into an existing course with minimal overhead,
can write their own content, use and modify content contributed by
others, customize the system, and collect data for educational studies.

@@

\section{Questions}

>>>>

Recent years have seen an explosion of online services for learning
to program:  Udacity \cite{udacity}, Codecademy \cite{codeacademy},
ProgZoo \cite{progzoo}, 
Codingbat \cite{codingbat}, Coursera \cite{coursera}, Turingscraft
\cite{turingscraft}, Problets \cite{Kumar:2005:GPA:1163405.1163408}, CS Circles \cite{Pritchard:2013:CCI:2445196.2445370} and
several others.  These systems are very powerful, and show great promise to
improve introductory computer science.  Given all of these
very good systems, one may ask why we thought
%it a good career move
%to build yet another system.
the world needed another such system.

%There are three main reasons:
%
%%\begin{itemize}
%
%%\item 
%First, we wanted a system that an instructor can easily integrate into an existing traditional course.
%  Many massive open online courses (MOOCs), such those available through Udacity and
%  Coursera, were not designed for a traditional classroom and cannot be easily incorporated into an existing course.  
%  The infrastructure provided by a MOOC is geared towards the course
%  taught through the MOOC, and is not really configurable or customizable.
%
% % systems, such as Udacity, Coursera, and CodeAcademy, are
% %  massive open online courses (MOOCs) that cannot be easily
% %  incorporated into a traditional classroom setting.  MOOCs can be wonderfully
% %  enriching for students who take these courses.  However, because
% %  MOOCs offer an entire
% %  course, whatever online programming infrastructure they provide is part of that
% %  course.
%
%%\item 
%Second, we wanted an open, customizable system that focuses on short programming exercises that students
%  can solve in their browser, and receive immediate feedback.  There are excellent systems that help
%  faculty manage longer programming assignments
%  \cite{Edwards:2008:WAG:1384271.1384371}, or homework and review questions
%  \cite{turingscraft, Kumar:2005:GPA:1163405.1163408}.  Codingbat
%  \cite{codingbat} is a fantastic free service that provides short
%  programming exercises, but it is not easily customizable and does not provide
%  access to all of the submissions submitted by students.
%  We see CloudCoder as a complementary component to these resources.
%
%% Some existing systems, such as Problets \cite{Kumar:2005:GPA:1163405.1163408},  and Turingscraft
%%   \cite{turingscraft}, provide homework exercises that can be incorporated
%%   such as Codingbat \cite{codingbat},
%%  , can be integrated into an existing course.
%%   Codingbat, while free to use and fantastically useful, does not give faculty access to a very
%%   rich data set
%
%%\item
%Finally, we wanted exercises that could be freely modified and
%redistributed.  Much of the excellent content available through MOOCs,
%or the increasing amount of digital content available through textbook publishers, 
%cannot be modified or re-used outside of those contexts.  This can be a significant
%impediment to researchers trying to study the difficulty level of
%various exercises, or to build intelligent tutoring systems (ITSs)
%that require a large bank of questions and their solutions.
%
%%\end{itemize}
%
%% There are two reasons.  First, many of
%% these systems, such are Udacity, Coursera, and CodeAcademy, are
%% massive open online courses (MOOCs).  MOOCs typically provide
%% supporting infrastructure that helps students learn to code in their
%% browsers, and the course material offered by a MOOC can be a wonderfully enriching
%% experience for someone who enrolls in the course.  However, it is not
%% clear how faculty who teach more traditional courses can
%% integrate any of the infrastructure provided by a MOOC into
%% their curriculum.  Second, 
%% the systems that could be easily integrated into an existing course, such as
%% Codingbat or Turingscraft, are
%% are either commercial, or closed, or both.  To our knowledge, none of
%% these systems readily support faculty who want to 
%% modify the code, host their own installation, extract data about
%% student behaviors beyond the basic correctness of their submissions,
%% or redistribute the programming exercises and assignments.
%
%We believe the academic community should have a fully open alternative
%to the closed and/or commercial systems that have exploded onto the CS
%Education scene.  Faculty can integrate CloudCoder into an existing course with minimal overhead,
%can write their own content, use and modify content contributed by
%others, customize the system, and collect data for educational studies.

Our primary motivation was {\em freedom}: we wanted a system where
the software and exercises could be freely redistributed, and
were not under the control of any central authority.  This motivation
is not entirely philosophical: we felt that locking down either
the software or the exercises would result in a barrier to adoption,
limiting the potential impact of the system.
As we will discuss in Section~\ref{sec:questions}, we think that there
are some interesting research questions that can be addressed
best through the existence of a ``free like air'' programming
exercise system: for example, we are very interested in finding out
whether exercises can be reused effectively in different courses
at different institutions.

Another motivation was a desire to collect data on students' work
on programming exercises as a way to study how students learn to program.
For example, CloudCoder captures a fine-grained edit history of each
student's work on each exercise.  Because the system is open source,
we (and other researchers) can easily add other kinds of data collection
to the system.

Finally, we wanted a system that supported a wide range of programming
languages.  For example, relatively few programming exercise systems
support C and C++.

@@

\section{Questions}\label{sec:questions}
